GO

### 2019-12-12 analysis/12_GO.Rmd
now with a few candidate genes

>>>>

```{r}
candidates <- c("AVP", "PRL", "PRLR", "GNIH",  "OXT", "AVPR1A", "AVPR1B",
                "CRH", "FSHB", "GH", "GNRH1", "GNRH2",
                "MC4R", "JAK2", "HCRT", "POMC", "TRH", "TSHB")
candidates <- as.data.frame(candidates)
names(candidates)[1] <- "gene"
candidates$GO <- "candidate genes"

candidate_DEGs <- left_join(candidates, DEGs) %>%
  arrange(GO, gene) %>%
  group_by(GO, comparison) %>%
  summarize(genes = str_c(gene, collapse = ", ")) %>%
  pivot_wider(names_from = comparison, values_from = genes) %>% 
  select(GO, contains("control.bldg"), contains("bldg.lay"), contains("lay.inc.d3"),
         contains("inc.d3.inc.d9"), contains("inc.d9.inc.d17"), contains("inc.d17.hatch"),
         contains("hatch.n5"), contains("n5.n9"))
candidate_DEGs <- as.data.frame(candidate_DEGs)
row.names(candidate_DEGs) <- candidate_DEGs$GO  
candidate_DEGs <- t(candidate_DEGs)
candidate_DEGs <- as.data.frame(candidate_DEGs)
candidate_DEGs <- tail(candidate_DEGs,10)
kable(candidate_DEGs)
